Risk Perceptions for Wearable Devices

### 2015-04-13 tex-inputs/methodology.tex
look over methodology

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 reading comprehension questions
\item 6 questions about wearable computing scenarios 
\item 2 questions about smartphone scenarios 
\item 2 Fischhoff-style risk/benefit questions 
\item 15 demographic questions \\[-.8cm]
\end{itemize}

@@

To ensure that participants had read and understood this device's capabilities, since it would form the basis for many of our survey questions, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn. We filtered out responses from participants who could not answer these questions.

\subsubsection{Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}). Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}. Questions were of the form:

@@

We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): \\[-.8cm]

@@

\begin{packed_item}
\item Your work contacts
\item Your friends
\item The public
\item The app's server (but didn't share it with anyone else)\\[-.8cm]
\end{packed_item}

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
\end{enumerate}

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies. We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.  These technologies were chosen to span varying levels of risks and benefits.

Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection. We asked about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities.

%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.

@@

\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]

\textit{Handguns}: \_\_\_\_\_\_\_ \\
\textit{Motorcycles}: \_\_\_\_\_\_\_\\
\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 reading comprehension questions
\item 6 questions about wearable computing scenarios 
\item 2 questions about smartphone scenarios 
\item 2 Fischhoff-style risk/benefit questions 
\item 15 demographic questions %\\[-.8cm]
\end{itemize}

@@

This device would form the basis for many of our survey questions. To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn. We filter out responses from participants who could not answer these questions.

\subsubsection{Wearable Scenarios}
We present scenarios involving data captured by the Cubetastic3000 and ask participants to rate how upset they would be if a particular type of data (e.g., video, audio, gestures, etc.) were shared without permission with a particular data recipient (see Figure \ref{fig:prompt}). Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''), following Felt \etal\cite{Felt}. Questions were of the form:

@@

We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>): %\\[-.8cm]

@@

\begin{packed_item}
\item Your work contacts
\item Your friends
\item The public
\item The app's server (but didn't share it with anyone else) %\\[-.8cm]
\end{packed_item}

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:

\begin{quotation}
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\it How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?}
\end{enumerate}
\end{quotation}

@@

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we examine broad perceptions of new technologies and how those compared to perceptions of other understood technologies. We model this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society. We ask participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity.  These technologies are chosen to span varying levels of risks and benefits.

Our goal was to ask about familiar technologies such as the Internet, general and specific wearable artifacts, and a range of new capabilities. To do this, we ask participants to evaluate one of 20 technologies relevant to wearables along 4 previously studied technologies. The 20 technologies are: Internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection.

@@

\begin{quotation}
{\it \noindent Fill in your <risk/benefit> numbers for the following:\\

\noindent Handguns: \_\_\_\_\_\_\_ \\
Motorcycles: \_\_\_\_\_\_\_\\
Lawnmowers: \_\_\_\_\_\_\_\\
<Wearable Technology>: \_\_\_\_\_\_\_\\
Electricity: \_\_\_\_\_\_\_\\ }
\end{quotation}
